\documentclass[12pt, a4paper, twoside, titlepage]{article}

\title{My First Article \thanks{To your mother}}

\author{Seonbin Kim  \\
	Seoul Compnay / University of Zurich  \\
	\and
	Sunny Choi \\
	Clock / University of Bern \\
	}

\date{\today}
% \date{\today} date coulde be today
% \date{25.12.00} or be a certain date
% \date{ } or there is no date

\begin{document}
% Hint: \title{what ever}, \author{who care} and \date{when ever} could stand
% before or after the \begin{document} command
% BUT the \maketitle command MUST come AFTER the \begin{document} command!

%doesn't show the title page without this
\maketitle


%%%%%%%%%%%%%%%%%%%%%%%% abstract


\begin{abstract}
I'll write short introduction of my paper here. xD \ldots
\end{abstract}

%\tableofcontents % create a table of contens



\section{Introduction}
Make it possible for all to write documents with \LaTeX{}!

\subsection{more introduction}
Go more in detail \ldots

\subsubsection{even more introduction}
come to the point \ldots

\paragraph{Paragraphs}
A paragraph is small but

\subparagraph{Subparagraphs}
subparagraphs are smaller!

\paragraph{Outline}
First we start with a little example of the article class, which is an
important documentclass. But there would be other documentclasses like
book \ref{book}, report \ref{report} and letter \ref{letter} which are
described in Section \ref{documentclasses}. Finally, Section
\ref{conclusions} gives the conclusions.



\section{Documentclasses} \label{documentclasses}

\begin{itemize}
\item article
\item book
\item report
\item letter
\end{itemize}


\begin{enumerate}
\item article
\item book
\item report
\item letter
\end{enumerate}

\begin{description}
\item[article\label{article}]{Article is \ldots}
\item[book\label{book}]{The book class \ldots}
\item[report\label{report}]{Report gives you \ldots}
\item[letter\label{letter}]{If you want to write a letter.}
\end{description}

\section{tabular}
No paper without a tabular!

\begin{tabular}{|l|c|r|p{2cm}|}
\hline
first column & second column & third column & fourth column \\
\hline
l stand for left & c for center & r for right & and p for predefined size \\
\hline
\end{tabular}


\section{some math}
Math in text is called in line math just put \$ character around
the math think. Like $ a^2 + b^2 = c^2 $. It looks better if you use
this
\[a^2 + b^2 = c^2\]

\section{Conclusions}\label{conclusions}
There is no longer \LaTeX{} example which was written by \cite{doe}.

\begin{thebibliography}{9}
\bibitem[Doe]{doe} \emph{First and last \LaTeX{} example.},
John Doe 50 B.C.
\end{thebibliography}

\end{document}
